Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-24 DGMM2025/paper.tex
Update figure 10

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{environ}
\usepackage{bbm}

@@

    \begin{figure}
        \begin{center}
            \begin{tabular}{|c||c|c|c|}
                \hline
                Curvature & II normals & CTriv normals & Our normals \\ \hline \hline
                $\kappa_1$ &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-NV}\\ \hline
                $\kappa_2$ &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-NV}\\ \hline
                $H$ &
                \includegraphics[width=0.3\textwidth]{pictures/d20-H-II} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-H-NV}\\ \hline
                $G$ &
                \includegraphics[width=0.3\textwidth]{pictures/d20-G-II} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-G-NV}\\ \hline
            \end{tabular}
        \end{center}
        \caption{Estimation of curvatures using Corrected Normal Current
        estimators \cite{lachaud:2022-dcg} for the shape ``Dice-20'' of Thingi10K
        database at resolution $256^3$. This estimator is
        parameterized by an input normal estimator: first column by
        ``Integral Invariant normals'' (radius $r=4.77$, second column
        by ``Convolved Trivial normals'' (radius $k=3$), third column
        by our presented normal estimator (radius $r=8.5$). Per row are displayed the
        estimated curvatures in order: first and second principal
        curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
            Gaussian curvature $G$. The range of curvature between deep
            blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
            color equal to $0$.}
    \end{figure}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{environ}
\usepackage{bbm}
%\usepackage{array}
%\usepackage{multirow}

@@

    \begin{figure}
        \begin{center}
            \begin{tabular}{|c||c|c|c|}
                \hline
                Curvature & II normals & CTriv normals & Our normals \\ \hline \hline
                \raisebox{18mm}{$\kappa_1$} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II.jpg} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv.jpg}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-k1-VN.jpg}\\ \hline
                \raisebox{18mm}{$\kappa_2$} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II.jpg} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv.jpg}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-k2-VN.jpg}\\ \hline
                \raisebox{18mm}{$H$} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-H-II.jpg} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv.jpg}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-H-VN.jpg}\\ \hline
                \raisebox{18mm}{$G$} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-G-II.jpg} &
                \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv.jpg}&
                \includegraphics[width=0.3\textwidth]{pictures/d20-G-VN.jpg}\\ \hline
            \end{tabular}
        \end{center}
        \caption{Estimation of curvatures using Corrected Normal
          Current estimators \cite{lachaud:2022-dcg} with a measure of
          radius $2$ for the shape ``Dice-20'' of Thingi10K database
          at resolution $256^3$. This estimator is parameterized by an
          input normal estimator: first column by ``Integral Invariant
          normals'' (radius $r=6$, second column by ``Convolved
          Trivial normals'' (radius $k=6$), third column by our
          presented normal estimator (deviation $\sigma=4$, radius
          $r=2\sigma=8$). Per row are displayed the estimated
          curvatures in order: first and second principal curvatures
          $\kappa_1$ and $\kappa_2$, mean curvature $H$, Gaussian
          curvature $G$. The range of curvature between deep blue and
          deep red is $\lbrack -0.1, 0.1 \rbrack$ with white color
          equal to $0$.}
    \end{figure}
